Impact of Roe v. Wade’s Overturn: Abortion Restrictions and Infant Mortality in the U.S. Using a Difference-in-Differences Analysis

### 2024-12-02 paper/ExaminingtheimpactOverturnofRoev.Wade:BanningofAbortiononInfantMortalityRatesintheUnitedStatesUsingaDifference-in-DifferencesApproach.qmd
update paper, pointing how to download raw data
update paper with new reference package

In this study, we utilized several R packages to streamline data
manipulation, modeling, and visualization. The `tidyverse` package
[@tidyverse] was central to our workflow, providing tools for data
wrangling and analysis, while `arrow` [@arrow] efficiently managed
parquet files for larger datasets. We used `modelsummary` package
[@modelsummary] to generate clean and interpretable summaries of our
regression models. We used `knitr` [@knitr] and `kableExtra`
[@kableExtra] to generate clean tables and reproducible reports, and
`usmap` for geographical visualizations. We use `here` [@here] package
simplifies the management of file paths, ensuring a reproducible
workflow by creating a consistent point of reference for file locations,
regardless of the operating system or working directory. Data cleaning
was facilitated by `janitor` [@janitor], while `lubridate` [@lubridate]
handled date-time variables. Visualization tasks were enhanced with
`ggplot2` [@ggplot2], and Bayesian regression modeling was conducted
using `rstanarm` [@rstanarm]. We use `fixest` [@fixest] to conduct the
event study. We use `caret` [@caret] to conduct the cross-validation of
the model. Together, these packages supported an efficient, reproducible
workflow for analyzing and presenting our findings.

@@

>>>>

In this study, we utilized several R packages to streamline data
manipulation, modeling, and visualization. The `tidyverse` package
[@tidyverse] was central to our workflow, providing tools for data
wrangling and analysis, while `arrow` [@arrow] efficiently managed
parquet files for larger datasets. We used `modelsummary` package
[@modelsummary] to generate clean and interpretable summaries of our
regression models. We used `knitr` [@knitr] and `kableExtra`
[@kableExtra] to generate clean tables and reproducible reports, and
`usmap` for geographical visualizations. We use `dplyr` [@dplyr] to manipulate data. We use `testthat` [@testthat] to test the simulated and analysis dataset. We use `usmap` [@usmap] to plot and analyze U.S. state and county-level data on maps by providing preformatted map geometries and easy integration with data. We use `here` [@here] package simplifies the management of file paths, ensuring a reproducible
workflow by creating a consistent point of reference for file locations,
regardless of the operating system or working directory. Data cleaning
was facilitated by `janitor` [@janitor], while `lubridate` [@lubridate]
handled date-time variables. Visualization tasks were enhanced with
`ggplot2` [@ggplot2], and Bayesian regression modeling was conducted
using `rstanarm` [@rstanarm]. We use `fixest` [@fixest] to conduct the
event study. We use `caret` [@caret] to conduct the cross-validation of
the model. Together, these packages supported an efficient, reproducible
workflow for analyzing and presenting our findings.

@@

## Raw Dataset Download

The complete process of downloading the raw dataset is shown in the `README.md` file.
